Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-04 nge.tex
down to 10!

As discussed in \S\ref{sec:panda_titan}, the absence of pilots imposes the
static coupling between MPI scripts submitted to the PBS batch system and
detector simulations. This makes the scheduling of multiple generations of
workload on the same PBS job impossible: Once a statically defined number of
detector simulations are packaged into a PBS job and this job is queued on
Titan, no further simulations can be added to that job. New simulations have to
be packaged into a new PBS job that needs to be submitted to Titan based upon
backfill availability.

@@

The NGE Agent uses the \emph{Open Run-Time Environment (ORTE)} for communication
and coordination of the execution of units. This environment is a critical
component of the OpenMPI implementation, developed to support distributed
high-performance computing applications operating in a heterogeneous
environment~\cite{castain05:_open_rte, cug-2016}.

ORTE provides a mechanism to create a \emph{``dynamic virtual machine''} (DVM)
that spans multiple nodes. The DVM transparently provides support for
interprocess communication, resource discovery and allocation, and process
launching across a variety of platforms. Libraries enable the interaction
between users and ORTE to enable the submission, monitoring and managing of
tasks, avoiding filesystem bottlenecks and race conditions with network sockets.
As a consequence, ORTE is able to minimize the system overhead while submitting
tasks.

>>>>

The absence of pilots imposes the static coupling between MPI scripts
submitted to the PBS batch system and detector simulations
(\S\ref{sec:panda_titan}). This makes the scheduling of multiple generations
of workload on the same PBS job impossible: once a statically defined number
of detector simulations are packaged into a PBS job and this job is queued on
Titan, no further simulations can be added to that job. New simulations have
to be packaged into a new PBS job that needs to be submitted to Titan based
upon backfill availability.

@@

The NGE Agent uses the \emph{Open Run-Time Environment (ORTE)} for
communication and coordination of the execution of units. This environment is
a critical component of the OpenMPI implementation, developed to support
distributed high-performance computing applications operating in a
heterogeneous environment~\cite{castain05:_open_rte, cug-2016}. ORTE provides
a mechanism to create a \emph{``dynamic virtual machine''} (DVM) that spans
multiple nodes. The DVM transparently provides support for interprocess
communication, resource discovery and allocation, and process launching across
a variety of platforms. Libraries enable the interaction between users and
ORTE to enable the submission, monitoring and managing of tasks, avoiding
filesystem bottlenecks and race conditions with network sockets. As a
consequence, ORTE is able to minimize the system overhead while submitting
tasks.
